---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.width=6.5, fig.height=2.8) 
# loading in relevant libraries
library(tidyverse)
library(dplyr, warn.conflicts = FALSE)
library(tidyr)
library(readxl)
library(data.table)
library(lubridate)
library(haven)
library(readxl)
library(ggplot2)
### Input data ###
income_race<-read.csv(here::here("outputs/data/race_income.csv"))
income_sex<-read.csv(here::here("outputs/data/sex_income.csv"))
```


```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-raceincome
#| fig-cap: "U.S. Income Distribution by Race"

# Make sure the order of the income level is the order we wanted
income_label <- c("LT $1000", "$1000 TO 2999", "$3000 TO 3999", "$4000 TO 4999", "$5000 TO 5999", "$6000 TO 6999", "$7000 TO 7999", "$8000 TO 9999", "$10000 - 14999", "$15000 - 19999", "$20000 - 24999", "$25000 OR MORE")
income_race$income <- 
  factor(income_race$income, 
         levels = income_label)

#generate graph#
ggplot(income_race, aes(x = income, y = the_number_of_people, fill = race)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(x = "Income level", y = "Numbers of people", title = "U.S. Income Distribution by Race") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 8))

```

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-raceincome
#| fig-cap: "U.S. Income Distribution by Sex"

# Make sure the order of the income level is the order we wanted
income_label <- c("LT $1000", "$1000 TO 2999", "$3000 TO 3999", "$4000 TO 4999", "$5000 TO 5999", "$6000 TO 6999", "$7000 TO 7999", "$8000 TO 9999", "$10000 - 14999", "$15000 - 19999", "$20000 - 24999", "$25000 OR MORE")
income_sex$income <- 
  factor(income_sex$income, 
         levels = income_label)

#generate graph#
ggplot(income_sex, aes(x = income, y = the_number_of_people, fill = sex)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(x = "Income level", y = "Numbers of people", title = "U.S. Income Distribution by Sex") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 8))


```

# Introduction

You can and should cross-reference sections and sub-sections. For instance, @sec-data and @sec-first-point. 



# Data {#sec-data}

Our data is of penguins (@fig-bills).

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

Also bills and their average (@fig-billssssss). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work.)

```{r}
#| label: fig-billssssss
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk way more about it. 



# Model

$$
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}
$$ {#eq-bayes}

@eq-bayes seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful. 

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional details


\newpage


# References


